<i>invivoPKfit</i> and <i>CvTdb</i> figures

### 2022-04-11 figures_01312022.Rmd
.

p <- ggplot(data = data,
            mapping = aes(x = sigma_value)) +
  geom_histogram(bins = 15) +
  # geom_density() +
  # scale_y_log10()+
  scale_x_log10() +
  theme_bw() +
  labs(x = "Sigma",
       y = "Number of observations") +
  facet_wrap(.~ model) +
  geom_vline(xintercept = 0.001476315)
# stat_function(fun = dlnorm, args = list(mean = mean(log(data$sigma_value)), sd = sd(log(data$sigma_value))))

>>>>

p <- ggplot(data = data,
            mapping = aes(x = sigma_value)) +
  geom_histogram(bins = 15) +
  # geom_density() +
  # scale_y_log10()+
  scale_x_log10() +
  theme_bw() +
  labs(x = "Sigma",
       y = "Number of observations") +
  facet_wrap(.~ model)
  # geom_vline(xintercept = 0.001476315)
# stat_function(fun = dlnorm, args = list(mean = mean(log(data$sigma_value)), sd = sd(log(data$sigma_value))))
